### 2014-07-29 Projects/Spartanburg_2014/Report/Spartanburg_2014.tex
Spartanburg 2014: Minor edit
Spartanburg: Add plan drawings of instrumentation

\headerB{
Spartanburg 2014
}

\headerC{
\flushright{
Daniel Madrzykowski \\
Craig G. Weinschenk \\
Kristopher J. Overholt \\
{\em Fire Research Division \\
Engineering Laboratory \\
Gaithersburg, Maryland, USA} \\ }
}

\flushright{\today \\
}

@@

\flushright{
\includegraphics[width=2.in]{../../../Bibliography/nistident_flright_vec} \\[.3in]
}

@@

@@

\begin{sidewaystable}[!ht]
\centering
\caption{Fuel masses}
\begin{tabular}{llcc}
\hline\noalign{\smallskip}
Item                         &  Material Description             &  Dimensions (m)            &  Mass (kg)  \\
\noalign{\smallskip}\hline\noalign{\smallskip}
% 3-seat Legacy Sofa         &  491 Brawley                      &  1.96 m x 0.86 m x 0.89 m  &  56.2 kg    \\
%   Cushion (left)           &  Cotton w/ inner springs          &                            &  4.06 kg    \\
%   Cushions (center)        &  Cotton w/ inner springs          &                            &  4.56 kg    \\
%   Cushions (rear)          &  Cotton w/ inner springs          &                            &  4.16 kg    \\
% 2-seat New Sofa            &  491 Brawley                      &  1.59 m x 0.91 m x 0.86 m  &  33.3 kg    \\
%   Cushion (seat)           &                                   &  0.56 m x 0.61 m x 0.14 m  &  1.6 kg     \\
%   Cushion (rear)           &  0.71 m at top, 0.58 m at bottom  &  Varies x 0.53 m x 0.20 m  &  2 kg       \\
3-seat Brown Sofa            &  302 College (front room)         &  2.24 m x 1.02 m x 0.91 m  &  61.0 kg    \\
2-seat Purple Stripe Sofa    &  302 College (front room)         &  1.57 m x 0.97 m x 0.86 m  &  82.0 kg    \\
3-seat Black Pine Leaf Sofa  &  302 College (front room)         &  2.08 m x 0.86 m x 0.86 m  &  51.0 kg    \\
Blue/Brown Chair             &  302 College (front room)         &  0.97 m x 0.81 m x 0.97 m  &  46.4 kg    \\
2-seat Floral Sofa           &  302 College (rear room)          &  1.68 m x 0.91 m x 0.91 m  &  34.5 kg    \\
2-seat Blue Plaid Sofa       &  302 College (rear room)          &  1.63 m x 0.97 m x 0.91 m  &  39.8 kg    \\
3-seat Yellow Sofa           &  302 College (rear room)          &  2.13 m x 0.91 m x 0.71 m  &  48.3 kg    \\
3-seat Floral Sofa           &  302 College (rear room)          &  2.29 m x 0.91 m x 0.91 m  &  48.0 kg    \\
3-seat New Sofa              &  289 College (front room)         &  2.13 m x 0.91 m x 0.91 m  &  43.0 kg    \\
Blue Chair                   &  289 College (middle room)        &  0.91 m x 0.91 m x 0.91 m  &  25.3 kg    \\
3-seat Floral Sofa           &  289 College (sprinkler room)     &  2.24 m x 1.02 m x 1.02 m  &  81.2 kg    \\
Floral Chair                 &  289 College (sprinkler room)     &  1.02 m x 1.02 m x 1.02 m  &  36.3 kg    \\
\noalign{\smallskip}\hline
\end{tabular}
\label{tab:Fuel_Masses}
\end{sidewaystable}

@@

\subsection{Test 3, Complete burndown}

\begin{figure}[!ht]
\includegraphics[width=5in]{../Figures/Script_Figures/305_Manning_Test_3_HF}
\caption{305 Manning, Test 3, Heat Flux}
\label{fig:305_Manning_Test_3_HF}
\end{figure}

>>>>

\begin{flushright}
\fontsize{20}{24}\selectfont
\bf{NIST Technical Note XXXX}
\end{flushright}

\headerB{
Spartanburg Fire Tests \\
2013--2014 \\
}

\normalsize

\headerC{
{
\flushright{
Daniel Madrzykowski \\
Kristopher J. Overholt \\
Craig G. Weinschenk \\

\vspace*{2\baselineskip}

\begingroup
\hypersetup{urlcolor=black}
\href{http://dx.doi.org/10.6028/NIST.TN.XXXX}{http://dx.doi.org/10.6028/NIST.TN.XXXX}
\endgroup
}

@@

\flushright{

\includegraphics[width=2.in]{../../../Bibliography/nistident_flright_vec} \\[.3in]
}
}
}

\newpage
\hspace{5in}
\newpage

\pagenumbering{roman}

\begin{flushright}
\fontsize{20}{24}\selectfont
\bf{NIST Technical Note XXXX}
\end{flushright}

\headerB{
Spartanburg Fire Tests \\
2013--2014 \\
}

\headerC{
\flushright{
Daniel Madrzykowski \\
Kristopher J. Overholt \\
Craig G. Weinschenk \\
{\em Fire Research Division \\
Engineering Laboratory} \\

\vspace*{2\baselineskip}

\begingroup
\hypersetup{urlcolor=black}
\href{http://dx.doi.org/10.6028/NIST.TN.XXXX}{http://dx.doi.org/10.6028/NIST.TN.XXXX} \\
\endgroup

\vspace*{2\baselineskip}

August 2014}}

\flushright{\includegraphics[width=1in]{../../../Bibliography/doc} }

@@

\section{Instrumentation}
\label{sec:Instrumentation}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Instrumentation/286_College}
\caption{Instrumentation, 286 College}
\label{fig:Instrumentation_286_College}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Instrumentation/489_N_Forest_1st_Floor}
\caption{Instrumentation, 489 N. Forest, first floor}
\label{fig:Instrumentation_489_N_Forest_1st_Floor}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Instrumentation/489_N_Forest_2nd_Floor}
\caption{Instrumentation, 489 N. Forest, second floor}
\label{fig:Instrumentation_489_N_Forest_2nd_Floor}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Instrumentation/302_College}
\caption{Instrumentation, 302 College}
\label{fig:Instrumentation_302_College}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Instrumentation/305_Manning}
\caption{Instrumentation, 305 Manning}
\label{fig:Instrumentation_305_Manning}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Instrumentation/289_Manning_1st_Floor}
\caption{Instrumentation, 305 Manning, first floor}
\label{fig:Instrumentation_305_Manning_1st_Floor}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Instrumentation/289_Manning_2nd_Floor}
\caption{Instrumentation, 305 Manning, second floor}
\label{fig:Instrumentation_305_Manning_2nd_Floor}
\end{figure}

@@

\begin{sidewaystable}[!ht]
\centering
\caption{Fuel masses}
\begin{tabular}{llcc}
\hline\noalign{\smallskip}
Item                         &  Material Description             &  Dimensions (m)            &  Mass (kg)  \\
\noalign{\smallskip}\hline\noalign{\smallskip}
% 3-seat Legacy Sofa         &  491 Brawley                      &  1.96 m x 0.86 m x 0.89 m  &  56.2 kg    \\
%   Cushion (left)           &  Cotton w/ inner springs          &                            &  4.06 kg    \\
%   Cushions (center)        &  Cotton w/ inner springs          &                            &  4.56 kg    \\
%   Cushions (rear)          &  Cotton w/ inner springs          &                            &  4.16 kg    \\
% 2-seat New Sofa            &  491 Brawley                      &  1.59 m x 0.91 m x 0.86 m  &  33.3 kg    \\
%   Cushion (seat)           &                                   &  0.56 m x 0.61 m x 0.14 m  &  1.6 kg     \\
%   Cushion (rear)           &  0.71 m at top, 0.58 m at bottom  &  Varies x 0.53 m x 0.20 m  &  2.0 kg     \\
3-seat Brown Sofa            &  302 College (front room)         &  2.24 m x 1.02 m x 0.91 m  &  61.0 kg    \\
2-seat Purple Stripe Sofa    &  302 College (front room)         &  1.57 m x 0.97 m x 0.86 m  &  82.0 kg    \\
3-seat Black Pine Leaf Sofa  &  302 College (front room)         &  2.08 m x 0.86 m x 0.86 m  &  51.0 kg    \\
Blue/Brown Chair             &  302 College (front room)         &  0.97 m x 0.81 m x 0.97 m  &  46.4 kg    \\
2-seat Floral Sofa           &  302 College (rear room)          &  1.68 m x 0.91 m x 0.91 m  &  34.5 kg    \\
2-seat Blue Plaid Sofa       &  302 College (rear room)          &  1.63 m x 0.97 m x 0.91 m  &  39.8 kg    \\
3-seat Yellow Sofa           &  302 College (rear room)          &  2.13 m x 0.91 m x 0.71 m  &  48.3 kg    \\
3-seat Floral Sofa           &  302 College (rear room)          &  2.29 m x 0.91 m x 0.91 m  &  48.0 kg    \\
3-seat New Sofa              &  289 College (front room)         &  2.13 m x 0.91 m x 0.91 m  &  43.0 kg    \\
Blue Chair                   &  289 College (middle room)        &  0.91 m x 0.91 m x 0.91 m  &  25.3 kg    \\
3-seat Floral Sofa           &  289 College (sprinkler room)     &  2.24 m x 1.02 m x 1.02 m  &  81.2 kg    \\
Floral Chair                 &  289 College (sprinkler room)     &  1.02 m x 1.02 m x 1.02 m  &  36.3 kg    \\
\noalign{\smallskip}\hline
\end{tabular}
\label{tab:Fuel_Masses}
\end{sidewaystable}

@@

% \clearpage

% Heat flux measurements are large negative values

% \subsection{Test 3, Complete burndown}

% \begin{figure}[!ht]
% \includegraphics[width=5in]{../Figures/Script_Figures/305_Manning_Test_3_HF}
% \caption{305 Manning, Test 3, Heat Flux}
% \label{fig:305_Manning_Test_3_HF}
% \end{figure}
